---
title: "Ass 3"
author: "Nyasha"
date: "7/2/2020"
output: pdf_document
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
if(!require(readr)) install.packages("readr", repos = "http://cran.us.r-project.org")
if(!require(FactoMineR)) install.packages("FactoMineR", repos = "http://cran.us.r-project.org")
if(!require(ggplot2)) install.packages("ggplot2", repos = "http://cran.us.r-project.org")
if(!require(dplyr)) install.packages("dplyr", repos = "http://cran.us.r-project.org")
if(!require(lubridate)) install.packages("lubridate", repos = "http://cran.us.r-project.org")
if(!require(data.table)) install.packages("data.table", repos = "http://cran.us.r-project.org")
if(!require(plotly)) install.packages("plotly", repos = "http://cran.us.r-project.org")
if(!require(gbm)) install.packages("gbm", repos = "http://cran.us.r-project.org")
if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(formattable)) install.packages("formattable", repos = "http://cran.us.r-project.org")
if(!require(naniar)) install.packages("naniar", repos = "http://cran.us.r-project.org")
if(!require(rattle)) install.packages("rattle", repos = "http://cran.us.r-project.org")
if(!require(shinythemes)) install.packages("shinythemes", repos = "http://cran.us.r-project.org")
if(!require(pROC)) install.packages("pROC", repos = "http://cran.us.r-project.org")
if(!require(rAverage)) install.packages("rAverage", repos = "http://cran.us.r-project.org")
if(!require(caTools)) install.packages("caTools", repos = "http://cran.us.r-project.org")
if(!require(glmnet)) install.packages("glmnet", repos = "http://cran.us.r-project.org")
library(knitr)
if(!require(cowplot)) install.packages("cowplot", repos = "http://cran.us.r-project.org")
if(!require(ROCR)) install.packages("ROCR", repos = "http://cran.us.r-project.org")
if(!require(caret)) install.packages("caret", repos = "http://cran.us.r-project.org")
if(!require(e1071)) install.packages("e1071", repos = "http://cran.us.r-project.org")
if(!require(neuralnet)) install.packages("neuralnet", repos = "http://cran.us.r-project.org")
if(!require(readxl)) install.packages("readxl", repos = "http://cran.us.r-project.org")
if(!require(h2o)) install.packages("h2o", repos = "http://cran.us.r-project.org")
```

# Exploratory Data Analysis


```{r}
framingham.assignment
sum(is.na(framingham.assignment))

# male, education, currentSmoker, BPMeds, prevalentStroke, prevalentHyp, diabetes, traintest, TenYearCHD should be factors

framingham.assignment$male <- as.factor(framingham.assignment$male)
framingham.assignment$education <- as.factor(framingham.assignment$education)
framingham.assignment$currentSmoker <- as.factor(framingham.assignment$currentSmoker)
framingham.assignment$BPMeds <- as.factor(framingham.assignment$BPMeds)
framingham.assignment$prevalentStroke <- as.factor(framingham.assignment$prevalentStroke)
framingham.assignment$prevalentHyp <- as.factor(framingham.assignment$prevalentHyp)
framingham.assignment$diabetes <- as.factor(framingham.assignment$diabetes)
framingham.assignment$traintest <- as.factor(framingham.assignment$traintest)
framingham.assignment$TenYearCHD <- as.factor(framingham.assignment$TenYearCHD)
# framingham.assignment$ <- as.factor(framingham.assignment$ )

str(framingham.assignment)

df1 <- framingham.assignment

unique(df1$cigsPerDay)

df1.st <- cbind(scale(df1[,c(2,5,10, 11, 12, 13, 14, 15)]), df1[,c(-2,-5,-10, -11, -12, -13, -14, -15)])

train <- filter(df1.st, traintest == "1")
test <- filter(df1.st, traintest == "0")

train <- select(train, -"traintest")
test <- select(test, -"traintest")

sum(is.na(train))
sum(is.na(test))

vis_miss(train)



```



```{r}
set.seed(1)
samp <- createDataPartition(train$TenYearCHD, times = 1, p = 0.8)

train_1 <- train[samp[["Resample1"]],]
validation <- train[-samp[["Resample1"]],]

vis_miss(train_1)
vis_miss(validation)


#
train_1 <- train_1 %>% drop_na()
validation <- validation %>% drop_na()


vis_miss(train_1)
vis_miss(validation)


```

```{r}

cor(train_1[,c(1:8)])

corrplot(train_1)

model1

```

## Support Vector Machines

```{r}


svm_model = svm(TenYearCHD ~. ,
                data = train_1,
                type = 'C-classification',
                kernel = "linear",
                scale = FALSE,
                cost = 1)
svm_model

svm_pred = predict(svm_model, train_1)
mean(svm_pred == train_1$TenYearCHD)

svm_pred1 = predict(svm_model, validation)
mean(svm_pred1 == validation$TenYearCHD)


svm_model = svm(TenYearCHD ~. ,
                data = train_1,
                type = 'C-classification',
                kernel = "radial",
                scale = FALSE,
                cost = 1)
svm_model

svm_pred = predict(svm_model, train_1)
mean(svm_pred == train_1$TenYearCHD)

svm_pred1 = predict(svm_model, validation)
mean(svm_pred1 == validation$TenYearCHD)

set.seed(1)
tunesvm = tune.svm(TenYearCHD~. ,
                   data = train_1,
                   type = 'C-classification',
                   kernel = c("radial"),
                   cost=seq(from=0.1, to=1 ,by=0.2))

tunesvm
bestmodel = tunesvm$best.model
bestmodel

svm_pred1 = predict(bestmodel, validation)
mean(svm_pred1 == validation$TenYearCHD)



```

## Neural Networks

```{r}

set.seed(1)

m <- model.matrix( ~ age +  cigsPerDay + totChol +  sysBP +  diaBP +   BMI   +  heartRate + glucose + male  + education +  currentSmoker +  BPMeds +  prevalentStroke + prevalentHyp + diabetes + TenYearCHD, data = train_1)


neuralnetmodel = neuralnet(TenYearCHD1 ~ age +  cigsPerDay + totChol +  sysBP +  diaBP +   BMI   +  heartRate + glucose ,
                           data = m,
                           err.fct = "ce",
                           linear.output = FALSE, 
                           act.fct = "logistic",
                           hidden = c(2))

folds <- createFolds(train_1$TenYearCHD, k = 10)
#results is a vector that will contain the accuracy for each of the network trainings and testing
results <- c()
for (fld in folds){
  #train the network
  set.seed(1)
  nn <- neuralnet(TenYearCHD~. ,
                           data = train_1,
                           hidden = c(2), 
                           err.fct = "ce", act.fct = "logistic",
                           linear.output = FALSE, stepmax = 1000000)
  
  #get the classifications from the network
  classes <- predict(nn, train_1[fld,])
  maxprobability <- apply(classes, 1, which.max) 
  valid.predict.class <- c('no', 'yes')[maxprobability] 
  
  results <- c(results, valid.predict.class== train_[fld,"Species"])
} 

results




```

```{r}

mod <- glm(TenYearCHD~.,data = train_1, family = binomial)
s1 <- summary(mod)
s1



train_a <- na.omit(train_1)
X <- data.matrix(train_a[,c(-16)])
Y <- data.matrix(train_a[16])

set.seed(1)
mod_a <- glmnet(X, Y, alpha = 1, nfolds = 10, type.measure = 'class', family = 'binomial')
set.seed(1)
cv <- cv.glmnet(X, Y, alpha = 1, nfolds = 10, type.measure = 'class', standardize = T, family = 'binomial')
plot(cv)

c1 <- coef(mod_a, s=cv$lambda.1se)
c2 <- coef(mod_a, s=cv$lambda.min)

mod_b <- glmnet(X, Y, alpha = 0.5, nfolds = 10, type.measure = 'class', family = 'binomial')
set.seed(1)
cv <- cv.glmnet(X, Y, alpha = 0.5, nfolds = 10, type.measure = 'class', standardize = T, family = 'binomial')
plot(cv)

(c3 <- coef(mod_b, s=cv$lambda.1se))
(c4 <- coef(mod_b, s=cv$lambda.min))


```
The general logistic regression model shows that age, cigsPerDay, sysBP, glucose and gender(male) are significant variables.

The Lasso regression model uses age, cigsPerDay, sysBP, glucose, gender(male), education, prevalentStroke, prevalentHyp and diabetes as the variables.

Elastic net model uses age, cigsPerDay, SysBP, diaBP, heartRate, glucose, male, education, PrevalentStroke, prevalentHyp, diabetes

## Facts 

All the three models use age, cigsPerDay, sysBP, glucose, gender(male)



```{r}
# pca <- PCA(train_1, ncp=5, graph=T)
# dimdesc(pca)
```

Look at correlation matrix
Use PCA and other variable selection techniques

```{r}

#localH2O = h2o.init(ip = "localhost", port = 54321, startH2O = TRUE,min_mem_size = "1g")
localH2O = h2o.init()
train.h2o <- as.h2o(train_1)
test.h2o <- as.h2o(validation)

hidden_opt <- list(c(3), c(2), c(1))
act <- c("Tanh", "Rectifier" )
l1_opt <- c(1e-5, 1e-7)
hyper_params <- list(hidden = hidden_opt, l1 = l1_opt, activation = act)

model_grid <- h2o.grid(
  "deeplearning",
  hyper_params = hyper_params,
  x = c(1,2,4,8,9,10, 13:15),
  y = 16,
  seed = 1, 
  reproducible = TRUE,
  distribution = "AUTO",
  balance_classes = TRUE,
  training_frame = train.h2o,
  validation_frame = test.h2o, nfolds=10)

model_grid
model1 = h2o.getModel(model_grid@model_ids[[1]])

c <- h2o.predict(model1 , test.h2o)
yhat = as.factor(as.matrix(c$predict))
confusionMatrix(yhat, validation$TenYearCHD)


## Selecting variables can help in deep learning



```